### 2011-04-11 Text/paper.tex
Finished with the benchmark pictures.
Second section editing.

\section{Numerical benchmark approach}
\label{sec:numerical:benchmark}
The main discussion here follows and is based on the two-dimensional benchmark approach
\cite{kuzmin-binary2d}. It was indicated that the benchmark layout should have certain
dimensions. Instead of using

\begin{tikzpicture}
%\draw (-2,-1,0,0)--(0,0,1);
%\draw (0,0,1)--(0,1,1);
\draw (-2,-1,0)--(2,-1,0)--(2,1,0)--(-2,1,0)--cycle;
\draw (-2,-1,0)--(-2,-1,1)--(2,-1,1)--(2,-1,0)--cycle;
\draw (-2,1,0)--(-2,1,1)--(2,1,1)--(2,1,0)--cycle;
\draw (-2,-1,1)--(2,-1,1)--(2,1,1)--(-2,1,1)--cycle;
\draw[rotate=90] (-2,0,0) circle (0.5);
%(Label(XY()*"$x$",align=-3Y));
%//surface s=surface(f,(0,0),(pi,2pi),100,Spline);
%draw("$z$",project(O--X),Arrow);
%draw("$y$",project(O--Y),Arrow);
%draw("$x$",project(O--Z),Arrow);
%//draw(YZ);
%label(project("W",Y,Z,(2,0,-0.3)));
%label(project("L",X,Z,(0,-1,-0.3)));
%label(project("H",Y,Z,(-2,-0.8,0.5)));
%draw(face1);
%draw(face2);
%draw(face3);
%draw(face4);
\end{tikzpicture}
\begin{tikzpicture}[line join=round]
\filldraw[draw=none,fill=white](-2,0)--(2,0)--(2,1)--(-2,1)--cycle;
\draw(2,0)--(2,1)--(-2,1)--(-2,0);
\filldraw[fill=white](-2,-.985)--(2,-.985)--(2,.985)--(-2,.985)--cycle;
\filldraw[fill=white](-2,-.985)--(-2,-1.158)--(2,-1.158)--(2,-.985)--cycle;
\filldraw[draw=none,fill=white](-2,0)--(-2,-1)--(2,-1)--(2,0)--cycle;
\draw(-2,0)--(-2,-1)--(2,-1)--(2,0);
\filldraw[fill=white](-2,1)--(-2,1)--(2,1)--(2,1)--cycle;
\filldraw[draw=none,fill=white](-2,-.087)--(-2,-1.158)--(2,-1.158)--(2,-.087)--cycle;
\draw(-2,-.087)--(-2,-1.158)--(2,-1.158)--(2,-.087);
\filldraw[fill=white](-2,-1)--(-2,-1)--(2,-1)--(2,-1)--cycle;
\filldraw[draw=none,fill=white](-2,.839)--(-2,-1)--(2,-1)--(2,.839)--cycle;
\draw(-2,.839)--(-2,-1)--(2,-1)--(2,.839);
\filldraw[fill=white](-2,.985)--(-2,.811)--(2,.811)--(2,.985)--cycle;
\filldraw[draw=none,fill=white](-2,.839)--(2,.839)--(2,1)--(-2,1)--cycle;
\draw(2,.839)--(2,1)--(-2,1)--(-2,.839);
\filldraw[draw=none,fill=white](-2,-.087)--(2,-.087)--(2,.811)--(-2,.811)--cycle;
\draw(2,-.087)--(2,.811)--(-2,.811)--(-2,-.087);
\end{tikzpicture}% End sketch output

>>>>

\section{Numerical benchmark approach}
\label{sec:numerical:benchmark}
The main discussion here follows and is based on the two-dimensional benchmark approach
\cite{kuzmin-binary2d}. It was indicated that the benchmark layout should have certain
dimensions to conduct simulations. The classical Bretherton benchmark layout is represented in Fig.
\ref{fig:classical:benchmark}. It describes the gas finger propagation through the liquid media.
The film thickness in this case is measured at the inlet. In lattice Boltzmann framework such
formulation has certain challenges \cite{kuzmin-binary2d}. Some of them are attributed to the
dynamic coupling of the inlet and outlet conditions \cite{giavedoni-numerical}. Instead, we
proposed the numerical benchmark indicated in Fig. \ref{fig:lbm:benchmark}. The dimensions of the
channel are chosen as $H_{\mathrm{eff}}\times H_{\mathrm{eff}} \times 15 H_{\mathrm{eff}}$. The
initialized bubble length is taken as $5 H_{\mathrm{eff}}$.\citet{giavedoni-numerical} showed that
the film stabilizes at the distances of $2.6-4.0$ diameters
from the front tip depending on the Reynolds number.  We chose to measure the film thickness in the
middle of the bubble, which is located at least at a distance of $2.5-3$ channel heights from the 
bubble tip. Moreover, the film thickness examination, see Section
\ref{section:film:thickness:variation}, shows that for the capillary range of interest, i.e.
$0.05\leq Ca \leq 1$, the standard deviation of the film thickness from the bubble middle film
thickness is around $7$
percent for small capillary numbers ($Ca=0.05$) and less than $1$ percent for larger ones ($Ca
\geq 0.1$). %at the distances one channel height from the rear tip upto one channel

This length of the bubble was shown as
sufficient for the film thickness to stabilize.

\begin{figure}[ht]
\includegraphics*[bb=153 610 405 717,width=\textwidth]{Figures/benchmark_classical.eps} 
\caption{The classical benchmark. The semiinfinite gas bubble
propagates through the liquid media. \label{fig:classical:benchmark}}
\end{figure}[ht]
\begin{figure}
\includegraphics*[bb=152 480 410 713,width=\textwidth]{Figures/benchmark_lbm.eps}
\caption{The classical benchmark. The semiinfinite gas bubble
propagates through the liquid media. \label{fig:lbm:benchmark}}
\end{figure}
